### 2018-09-09 Sections/network_algorithms.tex
new fig

>>>>

\begin{figure}[!hbtp]
\includegraphics[width=0.3\textwidth]{vehicle_routing_alg}
	\caption{Example of the vehicle routing problem, the multi-user generalisation of the shortest-path problem, where the goal is to minimise the total cost across all users. Intuitively, because whenever individual shortest-paths intersect one must trial different prioritisations, the combinatorics of this grow exponentially with the number of competing users.}\label{fig:VRS}
\end{figure}
